# Machine Learning in R: mlr Tutorial
This `r if (dev == "pdf") "document" else "web page"` provides an in-depth introduction to
the [Machine Learning in R: mlr](https://github.com/mlr-org/mlr) framework for machine
learning experiments in **R**.

We focus on the comprehension of the basic functions and applications.
More detailed technical information can be found in the [manual pages](%mlr) which
are regularly updated and reflect the documentation of the [current package version on CRAN](http://cran.r-project.org/web/packages/mlr/index.html).

An offline version of this tutorial is available for download

* [here](https://mlr-org.github.io/mlr-tutorial/release/mlr_tutorial.zip) for the
  current mlr release on CRAN and
* [here](https://mlr-org.github.io/mlr-tutorial/devel/mlr_tutorial.zip) for
  the mlr devel version on GitHub.

The tutorial explains the basic analysis of a data set step by step.
Please refer to sections of the menu above: Basics, Advanced, Extend and Appendix.

During the tutorial we present various simple examples from classification, regression, cluster and
survival analysis to illustrate the main features of the package.

Enjoy reading!

## Quick start
Applying a statistical algorithm with [%mlr] has a basic structure of 3 steps not depending on the specific model. 

```{r}
library(mlr)
data(iris)

## 1) Define the task
## specify the type of the analysis (e.g. classification)
task = makeClassifTask(id = "tutorial", data = iris, target = "Species")

## 2) Define the learner
## choose a specific algorithm.
lrn = makeLearner("classif.lda")

n = nrow(iris)
training.set = iris[seq(1, n, by = 2),]

## 3) Fit the model 
model = train(lrn, task, training.set)
```

```{r}
test.set = iris[seq(2, n, by = 2),]
pred = predict(model, task = task, subset = test.set)
```

```{r}
## Define the resampling strategy
rdesc = makeResampleDesc(method = "CV", stratify = TRUE)

## Do the resampling
r = resample(learner = lrn, task = task, resampling = rdesc, show.info = FALSE)

## Get the mean misclassification error
r$aggr
#> mmce.test.mean 
#>           0.02
```