# Exploring Learner Predictions

Learners use features to make predictions but how those features are used is often not apparent. [%mlr] can estimate the dependence of a learned function on a subset of the feature space using [&generatePartialPredictionData].

Partial prediction plots reduce the potentially high dimensional function estimated by the learner, and display a marginalized version of this function in a lower dimensional space. For example suppose $Y = f(X) + \epsilon$, where $\mathbb{E}[\epsilon|X] = 0$. With $(X, Y)$ pairs drawn independently from this statistical model, a learner may estimate $\hat{f}$, which, if $X$ is high dimensional can be uninterpretable. Suppose we want to approximate the relationship between some subset of $X$ (lower dimensional than $X$: possibly unidimensional). We partition $X$ into two sets, $X_s$ and $X_c$ such that $X = X_s \cup X_c$, where $X_s$ is a subset of $X$ of interest.

The partial dependence of $f$ on $X_c$ is:

$$f_{X_s} = \mathbb{E}_{X_c}f(X_s, X_c)$$

$X_c$ is integrated out. We use the following estimator:

$$\hat{f}_{X_s} = \frac{1}{N} \sum_{i = 1}^N \hat{f}(X_s, x_{ic})$$

The individual conditional expectation of an observation can also be estimated using the above algorithm absent the averaging, giving $\hat{f}^{(i)}_{X_s}$. This allows the discovery of features of $\hat{f}$ that may be obscured by an aggregated summary of $\hat{f}$. See [Goldstein, Kapelner, Bleich, and Pitkin (2014)](http://arxiv.org/abs/1309.6392) for more details and their package [ICEbox](https://cran.r-project.org/web/packages/ICEbox/index.html) for the original implementation. The algorithm works for any supervised learner with classification, regression, and survival tasks.

## Usage

### Generating Partial Predictions

Our implementation, following [%mlr]'s [visualization](visualization.md) pattern, consists of the above mentioned function [&generatePartialPredictionData], as well as two visualization functions, [&plotPartialPrediction] and [&plotPartialPredictionGGVIS]. The former generates input (objects of class `partialPredictionData`) for the latter.

The first step executed by [&generatePartialPredictionData] is to generate a feature grid for every element of the character vector `features` passed. The data are given by the `input` argument, which can be a [&Task] or a `data.frame`. The feature grid can be generated in several ways. A uniformly spaced grid of length `gridsize` (default 10) from the empirical minimum to the empirical maximum is created by default, but arguments `fmin` and `fmax` may be used to override the empirical default (the lengths of `fmin` and `fmax` must match the length of `features`). Alternatively the feature data can be resampled, either by using a bootstrap or by subsampling.

```{r}
lrn.classif = makeLearner("classif.ksvm", predict.type = "prob")
fit.classif = train(lrn.classif, iris.task)
pd = generatePartialPredictionData(fit.classif, iris.task, "Petal.Width")
pd
```

As noted above, $X_s$ does not have to be unidimensional. If it is not, the `interaction` flag must be set to `TRUE`. Then the individual feature grids are combined using the Cartesian product, and the estimator above is applied, producing a partial prediction for every combination of unique feature values. If the `interaction` flag is `FALSE` (the default) then by default $X_s$ is assumed unidimensional, and partial predictions are generate for each feature separately. The resulting output when `interaction = FALSE` has a column for each feature, and `NA` where the feature was not used in generating partial predictions.

```{r}
pd.lst = generatePartialPredictionData(fit.classif, iris.task, c("Petal.Width", "Petal.Length"), FALSE)
head(pd.lst$data)

tail(pd.lst$data)
```

```{r}
pd.int = generatePartialPredictionData(fit.classif, iris.task, c("Petal.Width", "Petal.Length"), TRUE)
pd.int
```

At each step in the estimation of $\hat{f}_{X_s}$ a set of predictions of length $N$ is generated. By default the mean prediction is used. For classification where `predict.type = "prob"` this entails the mean class probabilities. However, other summaries of the predictions may be used. For regression and survival tasks the function used here must either return one number or three, and, if the latter, the numbers must be sorted lowest to highest. For classification tasks the function must return a number for each level of the target feature.

As noted, the `fun` argument can be a function which returns three numbers (sorted low to high) for a regression task. This allows further exploration of relative feature importance. If a feature is relatively important, the bounds are necessarily tighter because the feature accounts for more of the variance of the predictions, i.e., it is "used" more by the learner.

```{r}
lrn.regr = makeLearner("regr.blackboost")
fit.regr = train(lrn.regr, bh.task)
pd.regr = generatePartialPredictionData(fit.regr, bh.task, "lstat", fun = median)
pd.regr
```

```{r}
pd.ci = generatePartialPredictionData(fit.regr, bh.task, "lstat", fun = function(x) quantile(x, c(.25, .5, .75)))
pd.ci
```

```{r}
pd.classif = generatePartialPredictionData(fit.classif, iris.task, "Petal.Length", fun = median)
pd.classif
```

As previously mentioned if the aggregation function is not used, i.e., it is the identity, then the conditional expectation of $\hat{f}^{i}_{X_x}$ is estimated. If `individual = TRUE` then `generatePartialPredictionData` returns $n$ partial predictions made at each point in the prediction grid constructed from the features.

```{r}
pd.ind.regr = generatePartialPredictionData(fit.regr, bh.task, "lstat", individual = TRUE)
pd.ind.regr
```

The resulting output, particularly the element `data` in the returned object, has an additional column `idx` which gives the index of the observation to which the row pertains.

For classification tasks this index references both the class and the observation index.

```{r}
pd.ind.classif = generatePartialPredictionData(fit.classif, iris.task, "Petal.Length", individual = TRUE)
pd.ind.classif
```

Individual partial predictions can also be centered by predictions made at all $n$ observations for a particular point in the prediction grid created by the features. This is controlled by the argument `center` which is a list  of the same length as the length of the `features` argument and contains the values of the `features` desired.

```{r}
iris = getTaskData(iris.task)
pd.ind.classif = generatePartialPredictionData(fit.classif, iris.task, "Petal.Length", individual = TRUE,
                                               center = list("Petal.Length" = min(iris$Petal.Length)))
```

### Plotting partial predictions

Results from [&generatePartialPredictionData] can be visualized with [&plotPartialPrediction] and [&plotPartialPredictionGGVIS].

With one feature and a regression task the output is a line plot, with a point for each point in the corresponding feature's grid.

```{r, fig.width = 8, fig.height = 4}
plotPartialPrediction(pd.regr)
```

With a classification task, a line is drawn for each class, which gives the estimated partial probability of that class for a particular point in the feature grid.

```{r, fig.width = 8, fig.height = 4}
plotPartialPrediction(pd.classif)
```

For regression tasks, when the `fun` argument of [&generatePartialPredictionData] is used, the bounds will automatically be displayed using a gray ribbon.

```{r, fig.width = 8, fig.height = 4}
plotPartialPrediction(pd.ci)
```

When multiple features are passed to [&generatePartialPredictionData] but `interaction = FALSE`, facetting is used to display each estimated bivariate relationship.

```{r, fig.width = 8, fig.height = 4}
plotPartialPrediction(pd.lst)
```

When `interaction = TRUE` in the call to [&generatePartialPredictionData], one variable must be chosen to be used for facetting, and a subplot for each value in the chosen feature's grid is created, wherein the other feature's partial predictions within the facetting feature's value are shown. Note that this type of plot is limited to two features.

```{r, fig.width = 8, fig.height = 8}
plotPartialPrediction(pd.int, facet = "Petal.Length")
```

[&plotPartialPredictionGGVIS] can be used similarly, however, since [%ggvis] currently lacks subplotting/facetting capabilities, the argument `interact` maps one feature to an interactive sidebar where the user can select a value of one feature.

```{r, eval = FALSE}
plotPartialPredictionGGVIS(pd.int, interact = "Petal.Length")
```

When `individual = TRUE` each individual conditional expectation curve is plotted.

```{r, fig.width = 8, fig.height = 4}
plotPartialPrediction(pd.ind.regr)
```

When the individual curves are centered by subtracting the individual conditional expectations estimated at a particular value of $X_s$ this results in a fixed intercept which aids in visualizing variation in predictions made by $\hat{f}^{(i)}_{X_s}$.

```{r, fig.width = 8, fig.height = 4}
plotPartialPrediction(pd.ind.classif)
```
